The Evolution of Phenotypically Invariant Genetic Networks

### 2017-02-07 kalman_walk.tex
added some notes on parameters/calculations helpful for computing DSD rates.

  \item \emph{(josh)} Add biology to introduction. (keep an eye out for concrete numbers we can use!) \jss{added some relevant biology citations to introduction. Still needs a lot of refinement.}

    \item Do some order-of-magnitude calculation to figure out how fast systems should drift.
        \begin{itemize}
            \item \emph{(peter)} Work out the math for how to do this.
            \item \emph{(josh)} Find real parameters to put into this.
        \end{itemize}

@@

\section{Background}

@@

\section{What biological question are we asking?}

@@

\section{How can we mathematically model this question?}

@@

\section{List of papers with some notes.}

>>>>

  \item \emph{(josh)} Add biology to introduction. (keep an eye out for concrete numbers we can use!) \jss{added some relevant biology citations to introduction. Still needs a lot of refinement.} \ref{sec:intro}

    \item Do some order-of-magnitude calculation to figure out how fast systems should drift.
        \begin{itemize}
            \item \emph{(peter)} Work out the math for how to do this.
            \item \emph{(josh)} Find real parameters to put into this. 
              \jss{added some notes for TFBS gain and loss calculations from Lynch} \ref{sec:param}
        \end{itemize}

@@

\section{Background} \label{sec:intro}

@@

\section{Estimates of network rewiring and developmenal systems drift.} \label{sec:param}

\jss{Parameter estimates for DSD $\downarrow$}

What parameters (and other relevant factors) do we need from the literature and experiment? 
  \begin{itemize}
    \item mutation rate
    \item Transcription factor binding site appearence and loss
    \begin{itemize}
      \item In \citep{lynch2007evolution} TF binding site gain ($u_{g}$) and loss ($u_{l}$) is estimated to be,
        \begin{align*}
          u_{g} &= \frac{(L-n+1)nu}{4^{n}} \\
          u_{l} &= nu
        \end{align*}
      Where $L$ is the length of the promoter, $n$ is the number of nucleotides in a TFBS, and $u$ is the mutation rate per base pair per generation. 
    \item \citet{lynch2007evolution} further states that in prokaryotes $L$ will usually be $\leq 100$ and in eukaryotes $L$ can range from $10^{3}$ to $10^{6}$. He also cites \citep{harbison2004transcriptional} that TFBSs range from $5-10$bps in length.
    \item in \citep{lynch2014evolutionary}, they estimate
        \begin{align*}
          \tilde{P}(m) = C \left[ 3^{\ell - m}  \left( \begin{array}{c} \ell \\ m \end{array} \right) \right] e^{2N_{e}s(m)}  ,
        \end{align*}
        where $\tilde{P}(m)$ is the stationary distribution of a TFBS with match (and strength) $m$. $C$ is the normalizer constant, $m$ is the number of matches, $\ell$ is the length of the TFBS motif. The term on the right is the ratio of fixation probabilities. 
        Or in their own words, there are two interpretations: 
        \begin{quote} ``(i) For a single TFBS, it represents the long-term proportion of evolutionary time spent in the various matching states and (ii) for a set of different TFBSs under the same selective constraints, it represents the expected distribution of states at any point in time.'' \end{quote}
      \item \citet{tuugrul2015dynamics, anderson2015intermolecular} also may be helpful.
    \end{itemize}
    \item rate of both \emph{trans-} and \emph{cis-} regulatory evolution. (see Sergey's papers).
      i.e. \citep{nuzhdin2004common, fear2016buffering, graze2009regulatory, graze2012allelic, genissel2008cis}
    \item The PWN-score landscape (does binding strength increase linearly, exponentially, have a threshold, etc.) with respect to SNPs.
    \item Others? 
  \end{itemize}

\section{(Old Notes) What biological question are we asking?}

@@

\section{(Old Notes) How can we mathematically model this question?}

@@

\section{(Old Notes) List of papers with some notes.}
